### 2015-10-01 manuscript.Rnw
add paragraph about fuzzy matching + synonyms

The function \texttt{tnrs\_match\_names} returns a data frame that lists the Open
Tree identifiers as well as other information to help users to ensure that the
taxa matched are the correct ones. Here, there is no ambiguity in the taxa
matched, however, as the Open Tree Taxonomy includes taxa from bacteria, plants,
and animals that are regulated by different nomenclatural codes (ICNP, ICN and
ICZN respectively), OTL and \texttt{rotl} provide tools to deal with potential
hemihomonyms. For instance, the argument \texttt{context\_name} can be used to
limit potential matches to a taxonomic group. The function
\texttt{tnrs\_contexts} provides a list of possible taxonomic contexts. When this
strategy cannot be used in case the tree encompasses multiple domains, the
functions \texttt{inspect} and \texttt{update} list alternative matches for a
taxon name, and replace it in the results, respectively. An example of this
approach is provided in the vignette ``How to use rotl?'' that accompanies the
package.

>>>>

The function \texttt{tnrs\_match\_names} returns a data frame that lists the Open
Tree identifiers as well as other information to help users to ensure that the
taxa matched are the correct ones. Here, there is no ambiguity in the taxa
matched, however, as the Open Tree Taxonomy includes taxa from bacteria, plants,
and animals that are regulated by different nomenclatural codes (ICNP, ICN and
ICZN respectively), OTL and \texttt{rotl} provide tools to deal with potential
hemihomonyms. For instance, the argument \texttt{context\_name} can be used to
limit potential matches to a taxonomic group. The function
\texttt{tnrs\_contexts} provides a list of possible taxonomic contexts. When this
strategy cannot be used in case the tree encompasses multiple domains, the
functions \texttt{inspect} and \texttt{update} list alternative matches for a
taxon name, and replace it in the results, respectively. An example of this
approach is provided in the vignette ``How to use rotl?'' that accompanies the
package.
By default, approximate matching is enabled when attempting to match taxonomic
names to their Open Tree Taxonomy identifiers. Additionally, taxonomic synonyms
are included in the Open Tree Taxonomy allowing researchers to match correct
identifiers for taxon names that might include misspellings or synonyms. These
features will facilitate the tedious data cleaning process often needed when
matching taxon names. In the example provided, both \textit{Escherichia coli}
and \textit{Saccharomyces cerevisiae} are misspelled but OTL's TNRS finds the
correct match for these taxa.
